Quantifying the manageability of pollination networks in an invasion context

### 2017-05-04 paper/manuscript.Rmd
Fix mathematical notation

* **Number of words:** 148 abstract; approx. 4,970 main text.

@@

Conveniently the information necessary to determine the minimum number of driver nodes *D* in a system with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015]. 
Such a system can be described by $\frac{dx}{dt} = Ax + Bu(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control vector), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively. 
If *S* is the number of species in the community, the matrix *A* has size $S \times $S whereas the matrix *B* has size $S \times D$.

The goal of structural controllability, which we employ here, is to use the information contained in $\mathbf{A}$ to generate a supportable estimate of $\mathbf{B}$ (and by extension $D$).
This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised. 
The trade-off is that, because of the assumption that ecological communities can be modeled with linear functional responses, structural controllability is not sufficient to fully design a the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another.	
Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].

@@

When exploring the effect of network structure itself, we observed that the driver-node density $n_D$ of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4). 
However, we found that the $n_D$ of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only in the direction of the asymmetries.

@@

Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species; instead, they are due to species properties that apply to invasive and native species alike (Table 1). 
Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest). 
To a smaller extent, visitation strength (a species' sum of visits) and degree also had a positive relationship with $f_S$. 
In contrast, the relationships between species structural properties and $f_D$ were less clear cut (Table 1). 
Both invasive species (which generally have a larger degree and high dependence strength) and pollinators (which generally have a smaller degree and low dependence strength) were classified as driver nodes in a large proportion of matchings.

>>>>

* **Number of words:** 148 abstract; approx. 5,006 main text.

@@

Conveniently the information necessary to determine the minimum number of driver nodes *D* in a system with linear dynamics is fully contained in the network structure [@Kalman1963; @Liu2011; @Motter2015]. 
Such a system can be described by $\frac{dx}{dt} = \mathbf{A}x + \mathbf{B}u(t)$, where the change of its state over time ($\frac{dx}{dt}$) depends on its current state *x* (for example, the species' abundances), an external time-varying input *u(t)* (the control signal), and two matrices *A* and *B*, which encode information about the network structure and how the species respond to the external input, respectively. 
If *S* is the number of species in the community, the matrix **A** has size $S \times S$ whereas the matrix **B** has size $S \times D$.

The goal of structural controllability, which we employ here, is to use the information contained in **A** to generate a supportable estimate of **B** (and by extension *D*).
This focus allows us to gain insight of the inherent controllability of a network, and the roles of the species that compose it, without being overly dependent on the particular choices of how the system dynamics are modelled or characterised. 
The trade-off is that, because of the assumption that ecological communities can be modelled with linear functional responses, structural controllability is not sufficient to fully design a the time-varying control signal *u(t)* that can drive the system from one particular equilibrium to another. 
Nevertheless, the lessons gained when assuming linearity---at both the network and the species level---are a prerequisite for understanding nonlinear control [@Liu2011; @Liu2016].

@@

When exploring the effect of network structure itself, we observed that the driver-node density *n~D~* of empirical networks was, in general, not significantly different to the manageability of network randomisations that maintained the degree of individual species (Figure 4). 
However, we found that the *n~D~* of empirical networks was significantly larger than that of randomisations that maintained the network structure but that differed only in the direction of the asymmetries.

@@

Invasive species were classified as superior nodes *and* driver nodes in every single network they were present; that is, they always had the highest relative *f~S~* and *f~D~* (Figure 5a). 
The model results suggest that these differences between invasive and native species are not underpinned by any intrinsic property of the invasive species; instead, they are due to species properties that apply to invasive and native species alike (Table 1). 
Specifically, we found that a species is more likely to be classified as a superior node if it had a large species strength (the sum of the dependences of all other species on the species of interest). 
To a smaller extent, visitation strength (a species' sum of visits) and degree also had a positive relationship with *f~S~*. 
In contrast, the relationships between species structural properties and *f~D~* were less clear cut (Table 1). 
Both invasive species (which generally have a larger degree and high dependence strength) and pollinators (which generally have a smaller degree and low dependence strength) were classified as driver nodes in a large proportion of matchings.
